Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2018-11-09 man/figures/correla_boot_sites.Rmd
create correla figure

##### 
**Figure 6.** Correlation coefficients obtained by relating tree-ring residual chronologies (RWI) of *Q. pyrenaica* and monthly climatic data: precipitation and 6-month SPEI (a), minimun (b) and maximun (c) temperatures. *green* bars: northern site (SJ); *light blue* bars: low-elevation southern site (CA-Low); and *dark blue* bars: high-elevation shouthern site (CA-High). Asteriks indicate significant ($P < 0.05$) correlation coefficients.

>>>>

##### 
**Figure S7.** Correlation among site chronologies (CA-High, CA-Low and SJ) in different time-domains after pre-filtering the time-series with increasing size of the moving-average window (1 to 40 years). Each site chronology was smoothed using centred moving averages with different window sizes (1 to 40 years), and then Pearson's correlation coefficient between the each pair chronologies were calculated. Significance was tested using 1000 boostrap replicates and with 95 % confidence intervals built using the R packgae `boot` [@Canty2016].

```{r}
correla  <- read.csv(file=here("/data/correla_ventanas_temporales/", "correla_chronos.csv"), header = TRUE)

correla <- correla %>% 
  mutate(
    name_comparison = as.factor(case_when(
      name_comparison == "caH-caL" ~ "CAHigh - CALow",
      name_comparison == "sj-caL" ~ "SJ - CALow",
      name_comparison == "sj-caH" ~ "SJ - CAHigh")))

correla_sitesSJCALH  <- correla %>% 
  filter(metodo_correla == 'pearson') %>%
  ggplot(aes(x=size, y=estimate, colour=name_comparison)) + 
  geom_line()+ theme_bw() + ylab('Correlation coefficient') +
  xlab('Smoothing (centred moving average window size)') + 
  # geom_smooth(method = 'loess', se=FALSE) + 
  theme(panel.grid = element_blank()) +
  geom_hline(yintercept = 0, colour='gray', linetype=2) + 
  geom_line(aes(x=size, y=ci_lower, colour=name_comparison), linetype = 2) +
  geom_line(aes(x=size, y=ci_upper, colour=name_comparison), linetype = 2) +
  theme(legend.position = c(.8,.9), legend.title = element_blank())

correla_sitesSJCALH
```
